Abstractions and exemplars: the measure noun phrase alternation in German

### 2018-01-06 Latex/sections/4experiments.tex
Mini fix.

The first experiment tests preferences for constructions explicitly in a forced choice task.
% \cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute 100 points between the alternatives, assigning more points to more natural sounding alternative.
% In essence, participants distribute a probability mass between two alternants, which is intended to produce more subtle results compared to a two-alternative forced-choice task such as in \cite{Rosenbach2013}, where participants have to choose one of two alternants.
% The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}.
% The criticism was reiterated in \cite{DivjakEa2016}, where they use a forced-choice task.
% In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge (with some numeric intricacies related to the non-linear distribution of preferences for alternants).
% I present a forced-choice experiment in this section instead of a split-100 experiment not only because of some researchers' critical attitude towards the split-100 task, but also because in a dry run of the experiment, participants complained about the unnaturalness of distributing a probability mass across two alternants and tended to produce ratings of 0 or 100 (or 50, although to a lesser degree).
Participants had to choose between two sentences that differed only in that one contained the \NACa\, and the other one contained the \PGCa.
The analysis compares the probabilities assigned to the stimuli by the corpus-derived model with the frequency with which participants chose the alternants.
There were 24 participants (native speakers of German without reading or writing disabilities) aged 19 to 30 living permanently in [NAME OF CITY REDACTED], who were recruited from introductory linguistics courses at [NAME OF UNIVERSITY REDACTED].
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper explicit knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary but participants received credit in partial fulfillment of course requirements.

>>>>

The first experiment tests preferences for constructions explicitly in a forced choice task.
% \cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute 100 points between the alternatives, assigning more points to more natural sounding alternative.
% In essence, participants distribute a probability mass between two alternants, which is intended to produce more subtle results compared to a two-alternative forced-choice task such as in \cite{Rosenbach2013}, where participants have to choose one of two alternants.
% The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}.
% The criticism was reiterated in \cite{DivjakEa2016}, where they use a forced-choice task.
% In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge (with some numeric intricacies related to the non-linear distribution of preferences for alternants).
% I present a forced-choice experiment in this section instead of a split-100 experiment not only because of some researchers' critical attitude towards the split-100 task, but also because in a dry run of the experiment, participants complained about the unnaturalness of distributing a probability mass across two alternants and tended to produce ratings of 0 or 100 (or 50, although to a lesser degree).
Participants had to choose between two sentences that differed only in that one contained the \NACa\, and the other one contained the \PGCa.
The analysis compares the probabilities assigned to the stimuli by the corpus-derived model with the frequency with which participants chose the alternants.
There were 24 participants (native speakers of German without reading or writing disabilities) aged 19 to 30 living permanently in [name of city redacted], who were recruited from introductory linguistics courses at [name of university redacted].
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper explicit knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary but participants received credit in partial fulfillment of course requirements.
